\documentclass[a4paper]{article}
\usepackage{titling}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage[margin=2.5cm]{geometry}

\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue
}

\usepackage{titlesec}
\titleformat{\section}
{\LARGE\bfseries}
{}
{0em}
{}[\titlerule]

\titleformat{\subsection}
{\large\bfseries}
{}
{0em}
{}

\renewcommand{\maketitle}{
  \begin{center}
  {\huge\bfseries\theauthor}

  \vspace{1em}
  %PLUG_CONTACT
    email: wisa.pow@gmail.com | phone: 085-936-5127 | github: \href{https://github.com/wisaTong}{wisaTong}
  \end{center}
}

\begin{document}
\title{R\'esum\'e}
\author{Wisa Powthongchin}

\pagenumbering{gobble}
\maketitle

%PLUG_EXPERIENCE
\section{Experiences}
\begin{itemize}[font=\itshape, leftmargin=4cm, itemsep=.75em, labelsep=2em]
  \item[Jun 2020|Nov 2020]\textbf{\large Kasikorn Business and Technology Group (KBTG)}

    Worked on batch processing using Golang.
  \item[Jun 2019|Sep 2019]\textbf{\large VISTEC}

    Worked on internal projects using Node.js, React, Vue, and Django. During
    the internship period, also exposed to several NLP and machine learning
    researches. 
  \item[Feb 2019|May 2019]\textbf{\large Senate System Corp}

    Developed a mobile application on both Android and IOS using Java and Swift
    respectively. 
  \item[Jun 2018|Sep 2018]\textbf{\large Billme co.}

     Developed micorservices using Scala writing in functional programming
     style. 
\end{itemize}

%PLUG_EDUCATION
\section{Education}
\subsection{Bachelor's Degree|Software and Knowledge Engineering}
Kasetsart University, Faculty of Engineering, Software and Knowledge Engineering program.

\section{Skills}
\subsection{Programming Language that I'm happy working with}
\begin{multicols}{2}
  \begin{itemize}
    \item Rust
    \item Golang
    \item Scala
    \item Javascript
  \end{itemize}
\end{multicols}
Happy to learn new languages.
\subsection{Linux}
Currently run Gentoo Linux on my main machine and laptop. Have good knowledge
of shell commands and GNU utility programs. 

\subsection{Other}
\begin{itemize}
  \item Container Technology|Hand-on experiences with Docker. Have good
    knowledge and deep understanding of how container works from working on 4th
    year final project at Kasetsart University.

  \item CI/CD|Have written Gitlab-CI pipeline for deploying container to
    development, staging, and production environment. 

  \item Google Cloud Platform|Real world experience setting up CloudRun,
    CloudSQL instances, and CloudStorage for a project, and little bit of
    experience on Kubernetes from university project. 
\end{itemize}


\end{document}
